%!TEX root = ../dissertation.tex
\begin{savequote}[75mm]
A good idea is about ten percent and implementation and hard work, and luck is 90 percent.
\qauthor{Guy Kawasaki}
\end{savequote}

\chapter{Implementation}
This chapter is about the implementation with Apache Storm to solve the defined queries.
The idea of the test scenario is to use "OSM Augmented Diffs" as a stream.
This diffs extend the ordinary minutely diffs of OSM with more information.
The result contains all the nodes, ways and relations changed durring the time periode.

\section{Queries}
The following list is about the queries which has to be done on the Augmented Diff stream.

\begin{itemize}
\item[A)] Leader board of top 10 OSM active users
\item[B)] Leader board of top 10 OSM objects added
\item[C)] Node objects with suspicious keys and values
\item[D)] Way objects with only user tag "area=yes" without other user tags
\end{itemize}

\section{A) Leader board of top 10 OSM active users}
It's about users who created or updated any OSM nodes all around the world.
The users are identified with by the tags "uid" and "user".

\section{B) Leader board of top 10 OSM objects added}
Count all the created or updated nodes grouped by a combination of key and value.
An example for this is "amenity=bench".

\section{C) Node objects with suspicious keys and values}
Detection of vandalism and unwanted bad actions in OpenStreetMap is a very difficult topic.
Thus we focus on "Quality Assurance Monitoring" by filtering for suspicious tags of node or way elements.
As an example for this issues are ";" in Tags like "crossing=island;uncontrolled".

\section{D) Way objects with only user tag "area=yes" without other user tags}
The point D) also deals with the vandalism problems.



